Manuscript draft

### 2019-09-12 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

---
title: "Manuscript draft"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene Muller-Landau, [MORE??-CHECK], Kristina J. Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("C:/Users/banburymorganr/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/S1.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, booktabs = TRUE, caption = "Hypothesis table", escape = F)
```

>>>>

---
title: "Manuscript draft"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene Muller-Landau, [MORE??-CHECK], Kristina J. Anderson-Teixeira"
output:
  pdf_document:
    includes:
      after_body: outline.md
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}

@@
